### 2021-09-10 analysis_and_paper/manuscript.Rmd
Adds IPA-note to manuscript.
Preparations for Experiment 2 data collection

note: |
  \clearpage

@@

otm1_incomplete_data <- otm1_n_trials$ParticipantNumber[
  with(
    otm1_n_trials
    , Eval != 2 ||
      RT != 160 ||
      NumbercorrectIdent != 1
  )
]

>>>>

note: |
  This manuscript has been accepted in-principle as a registered report at *Psychological Science*. Data for Experiment 2 will be collected when the SARS-CoV-2 pandemic permits.
  \clearpage

@@

otm1_incomplete_data <- otm1_n_trials %>% 
  rowwise %>% 
  mutate(
    incomplete = (Eval != 2 || RT != 160 || NumbercorrectIdent != 1)
  ) %>% 
  filter(incomplete) %>% 
  pull(ParticipantNumber)

### 2021-09-10 analysis_and_paper/supplements.Rmd
Preparations for Experiment 2 data collection

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "22") +
  geom_vline(xintercept = 0.5, linetype = "22") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "eiv_lm", color = "black") +
  # geom_smooth(method = "lm", color = "black") +
  labs(
    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  scale_x_continuous(trans = "probit") +
  theme_apa()
```

@@

otm1_iat_delta_eiv_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = qnorm(Accuracy)) %>%
  eiv_lm(delta ~ Accuracy, data = ., n.optim = 10) %>% 
  apa_print
```

>>>>

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "22") +
  geom_vline(xintercept = 0.5, linetype = "22") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "eiv_lm", color = "black", method.args = list(n.optim = 50)) +
  # geom_smooth(method = "lm", color = "black") +
  labs(
    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  scale_x_continuous(trans = "probit") +
  theme_apa()
```

@@

otm1_iat_delta_eiv_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = qnorm(Accuracy)) %>%
  eiv_lm(delta ~ Accuracy, data = ., n.optim = 50) %>% 
  apa_print
```
